---
title: "NSAC Alpinism"
author: "Lauke"
date: "20/01/2022"
output: ioslides_presentation
logo: Logo-ribbon.png
bibliography: references.bib
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
library(plotly)
library(bibtex)
```

```{r echo = F}
set.seed(123)
```


```{r echo = F, message=F, warning=F}
ID <- c(1:30)
exp_years <- round(rnorm(30, 5, 1), digits = 0)
mnts_climbed <- 0.8*exp_years + round(rnorm(30, 10, 5), digits = 0)
fun_had <- round(0.6*exp_years + 0.8*mnts_climbed + rnorm(1, 0, 1), digits = 0)

bergdat <- as.data.frame(cbind(ID, exp_years, mnts_climbed, fun_had))
```


## What's this about then

This is a template shitty presentation about how awesome mountains are and how dope the people at the Nederlandse Studenten Alpen Club are for trying to climb them. 

Check out the website of the NSAC at <https://nsac.alpenclub.nl/>.

## So what are mountains again?

<center> 
<img src = "Mountain.jpg" width = 90%>
</center>


## Carefully collected data

```{r echo = F}
datatable(bergdat, options = list(pageLength = 5), caption = "Mountain climbers dataset")
```
## Data generation

```{r eval = F}
ID <- c(1:30)
exp_years <- round(rnorm(30, 5, 1), 
                   digits = 0)
mnts_climbed <- 0.8*exp_years + round(rnorm(30, 10, 5), 
                                      digits = 0)
fun_had <- round(0.6*exp_years + 0.8*mnts_climbed + rnorm(1, 0, 1), 
                 digits = 0)

bergdat <- as.data.frame(cbind(ID, exp_years, mnts_climbed, fun_had))
```


## Careful analysis of this dataset
```{r echo = F}
p <- bergdat %>%
  ggplot(aes(x = exp_years)) +
  geom_histogram(binwidth = 1, colour = "black", fill = "forestgreen") +
  labs(title="Experience histogram plot",x="Experience(years)", y = "Count")

ggplotly(p)

```
## Course information {.columns-2}

C1: \
- Het leren voortbewegen in alle soorten basisterrein (rots, sneeuw, ijs, gletsjer) \
- Inschatting en perceptie van alpiene gevaren \
- Reddingstechnieken: gletsjerspleetredding (seirolle,prusiktechniek en Münchhausen) \
- Het zelfstandig kunnen maken van F/L-toeren \

C2: \
- Voortbewegen in 2e– en 3e-graads terrein \
- Het leren klimmen van (rots)graten \
- Inschatting en perceptie van alpiene gevaren \
- Zelfstandig kunnen maken van PD/WS touren \

[@nsac]


## It has some hard core science to it {.flexbox .vcenter}

<center>

$$
\begin{align}
Mount &= \beta_0 + \beta_1 Exp \;, \\
Fun &= \beta_0 + \beta_1 Exp + \beta_2 Mount\;. \\
\end{align}
$$

</center>

## References



```{r include = F}
sessionInfo()
```

